A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-21 4_method.tex
lil

\section{Method}
When performing the naive method of offsetting the outline inward with constant width paths the overfill and underfill problems arise in the center.
Constant widths inward steps might not resolve to the arbitrary width of the outline shape.
Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
We decide on a bead count at locations which lie in central positions of the shape in some sense to be defined below and apply an optimal distribution of widths from the central regions outward.

>>>>

\section{Method}
When performing the naive method of offsetting the outline inward with constant width paths the overfill and underfill problems arise in the center.
Constant widths inward steps might not resolve to the arbitrary width of the outline shape.
Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
We decide on a bead count at locations which lie in central positions of the shape and apply an optimal distribution of widths from the central regions outward.
